\vspace{-0.25em}\thetitle

### 2009-07-29 paper.tex
...

% It seems wise at this point to address the nature of prediction for highly nondeterministic phenomena like network traffic.
% Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
% flows may exhibit the same initial behavior but subsequently behave quite differently.
% The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.
% When compared with a specific outcome, such a prediction cannot be said to be ``wrong'' or ``right.''
% How then can one measure the quality of a predicted distribution of outcomes?
% This subtle and difficult issue is central to our evaluation methodology.

@@

>>>>

@@

% It seems wise at this point to address the nature of prediction for highly nondeterministic phenomena like network traffic.
Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
flows may exhibit the same initial behavior but subsequently behave quite differently.
The best we can hope to do is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.
When compared with a specific outcome, such a prediction cannot be said to be unequivocally ``wrong'' or ``right.''
How then can one measure the quality of a predicted distribution of outcomes?
This subtle and difficult issue is central to our evaluation methodology.
